New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2023-01-20 paper/appendix.Rmd

# Now set a new position
vchange <- 3
eps <- 0.1
plot_basis(A, vchange, vcol="black")

@@

# Iterate and save images
# Unconstrained orthonormalisation
Anew <- A
for (i in 1:3) {
  Anew[vchange,] <- A[vchange,]*(1-i*eps)
  exact <- Anew[vchange,]
  Anew <- orthonormalize_rotated(Anew, vchange)
  plot_basis(Anew, vchange, vcol="black")
  points(exact[1], exact[2], pch=16, col="orange")
}

>>>>

# Now set a new position
vchange <- 3
eps <- 0.1
plot_basis(A, vchange, vcol="black")
text(A[vchange, 1], A[vchange, 2], expression(V[m]), pos=3, col="orange")

@@

# Iterate and save images
# Unconstrained orthonormalisation
Anew <- A
for (i in 1:3) {
  Anew[vchange,] <- A[vchange,]*(1-i*eps)
  exact <- Anew[vchange,]
  Anew <- orthonormalize_rotated(Anew, vchange)
  plot_basis(Anew, vchange, vcol="black")
  points(exact[1], exact[2], pch=16, col="orange")
  text(Anew[vchange, 1], Anew[vchange, 2], expression(V[m]), pos=3, col="orange")

}

### 2023-01-20 paper/paper.Rmd

We start by a comparison of the two models and the data distribution shifting to $\mathbf{c}^{+}$, thus the slice is localized towards high values of bill depth in top row of Figure \ref{slice1p}. The star glyph at right indicates the slice center value, which shows that it is higher on `bd` and at the middle value for the other variables. This slice center guide is as proposed in @condviz2, and more details can be found in the Appendix. We can see that all three slices (the two models and the data) contain almost no points from the third class (Gentoo), and that the decision boundary between the two models is very similar.

@@

A more interesting comparison is found for $\mathbf{c}^{-}$, thus the slice localized towards low values of bill depth, shown in the bottom row of Figure \ref{slice1p}. (The star glyph at right indicates the slice center value, which shows that it is lower on `bd` and at the middle value for the other variables.) The RF model (left) predicts all three species within this slice, with an interesting boundary for the third class (Gentoo). On the other hand the LDA model (middle) predominantly predicts the third class within the slice, this appears to be enforced through the linear structure of the model. Looking finally at the thick slice through the data we see that there are primarily observations from this class within the slice we can conclude that the two models have filled in the "empty" space (where we do not have any training observations) in very different ways and according to what we might expect given the model structure.

>>>>

We start by a comparison of the two models and the data distribution shifting to $\mathbf{c}^{+}$, thus the slice is localized towards high values of bill depth in top row of Figure \ref{slice1p}. \textcolor{blue}{The star glyph at right indicates the slice center value, which shows that it is higher on `bd` and at the middle value for the other variables. This slice center guide is as proposed in @condviz2, and more details can be found in the Appendix.} We can see that all three slices (the two models and the data) contain almost no points from the third class (Gentoo), and that the decision boundary between the two models is very similar.

@@

A more interesting comparison is found for $\mathbf{c}^{-}$, thus the slice localized towards low values of bill depth, shown in the bottom row of Figure \ref{slice1p}. \textcolor{blue}{(The star glyph at right indicates the slice center value, which shows that it is lower on `bd` and at the middle value for the other variables.)} The RF model (left) predicts all three species within this slice, with an interesting boundary for the third class (Gentoo). On the other hand the LDA model (middle) predominantly predicts the third class within the slice, this appears to be enforced through the linear structure of the model. Looking finally at the thick slice through the data we see that there are primarily observations from this class within the slice we can conclude that the two models have filled in the "empty" space (where we do not have any training observations) in very different ways and according to what we might expect given the model structure.

### 2023-01-20 paper/paper.tex

We start by a comparison of the two models and the data distribution
shifting to \(\mathbf{c}^{+}\), thus the slice is localized towards high
values of bill depth in top row of Figure \ref{slice1p}. We can see that
all three slices (the two models and the data) contain almost no points
from the third class (Gentoo), and that the decision boundary between
the two models is very similar.

@@

A more interesting comparison is found for \(\mathbf{c}^{-}\), thus the
slice localized towards low values of bill depth, shown in the bottom
row of Figure \ref{slice1p}. The RF model (left) predicts all three
species within this slice, with an interesting boundary for the third
class (Gentoo). On the other hand the LDA model (middle) predominantly
predicts the third class within the slice, this appears to be enforced
through the linear structure of the model. Looking finally at the thick
slice through the data we see that there are primarily observations from
this class within the slice we can conclude that the two models have
filled in the ``empty'' space (where we do not have any training
observations) in very different ways and according to what we might
expect given the model structure.

>>>>

We start by a comparison of the two models and the data distribution
shifting to \(\mathbf{c}^{+}\), thus the slice is localized towards high
values of bill depth in top row of Figure \ref{slice1p}.
\textcolor{blue}{The star glyph at right indicates the slice center value, which shows that it is higher on `bd` and at the middle value for the other variables. This slice center guide is as proposed in @condviz2, and more details can be found in the Appendix.}
We can see that all three slices (the two models and the data) contain
almost no points from the third class (Gentoo), and that the decision
boundary between the two models is very similar.

@@

A more interesting comparison is found for \(\mathbf{c}^{-}\), thus the
slice localized towards low values of bill depth, shown in the bottom
row of Figure \ref{slice1p}.
\textcolor{blue}{(The star glyph at right indicates the slice center value, which shows that it is lower on `bd` and at the middle value for the other variables.)}
The RF model (left) predicts all three species within this slice, with
an interesting boundary for the third class (Gentoo). On the other hand
the LDA model (middle) predominantly predicts the third class within the
slice, this appears to be enforced through the linear structure of the
model. Looking finally at the thick slice through the data we see that
there are primarily observations from this class within the slice we can
conclude that the two models have filled in the ``empty'' space (where
we do not have any training observations) in very different ways and
according to what we might expect given the model structure.
